\textbf{Autoreduction - an automated data reduction system for beamline instruments at the ISIS Facility}

### 2017-07-12 Documentation/paper/paper.tex
Updated deployment section

The system is deployed at ISIS. The node managing
the state and web app is a Windows Server system running on a 
Hyper-V\cite{hyper-v} virtualisation cluster; it serves the web app using
Microsoft's Internet Information Services (IIS)\cite{iis} and 
FastCGI\cite{fcgi}. The web app is currently only accessible from inside
the laboratory using the URL: http://reduce.isis.cclrc.ac.uk.

There is one reduction node, running Red Hat Enterprise Linux 7\cite{rhel}
on a dedicated server -- reducing large amounts of data is memory and CPU-intensive.
This node also serves the message queue; subsequent worker nodes would
not have multiple message queues, and the message queue will be hosted
on a separate node.

@@

\begin{enumerate}
\item
  Expanding the system to accommodate greater volume of use -- this
  might involve accomodating more reduction workers, for example
\item
  Integrating other methods of monitoring or listening for new runs -- the current
  method of watching a file archive is specific to ISIS
\item
  Make the web app to be accessible from outside of the laboratory
\item
  Have selected reduced data automatically cataloqued in ICAT 
\item
  Improving portability and deployability of the current software; the
  state database/webapp is currently somewhat nontrivial to deploy
\end{enumerate}

Longer term, the system may be extended to listen to live streams and starts
processing such data as they come off beamlines rather then waiting for files 
to be written to disk.

@@

The autoreduction system offers a convenient way of automating data reduction
on beamline instruments. It uses a scalable architecture to allow prompt
reduction of data from a large number of instruments, and utilises a web app
frontend to allow users to control the reduction process manually and verify
that the correct reduction was executed.

@@

@@

>>>>

The system is deployed at ISIS. The node managing the WebApp is a Windows Server 2012
running on a Hyper-V\cite{hyper-v} virtualisation cluster and it serves the WebApp using
Apache's HTTP Server\cite{apache}. The WebApp runs on a Windows server for security reasons
but since it runs on a basic Apache server, it could easily be moved across to a Linux machine
if it needed to. The WebApp is currently only accessible from inside the laboratory using the 
URL: http://reduce.isis.cclrc.ac.uk.

There is then a second node which runs Red Hat Enterprise Linux 7\cite{rhel}. This node
manages the parts of the system which are common between front and backend. This includes:
the MySQL database, the ActiveMQ server and the EndOfRunMonitor. This node should have
all the parts of the system that wouldn't need to be replicated as part of a worker node.

The third and final node manages the parts of the system that could be replicated such that 
we can have multiple worker nodes active in order to split the load of autoreduction and speed
up the overall process. This node has the QueueProcessor and the AutoreductionProcessor installed
on it. At the moment, the production system only uses one of these nodes but as the usage of the 
system increases, so too will the load. It might then be sensible to have multiple worker nodes.

The system is split out in this way such that if the machine with the WebApp installed were to fail,
the overall process of reduction could still take place. We would still pick up new runs with the 
EndOfRunMonitor and would still be able to process them with QueueProcessor and AutoreductionProcessor.

@@

\begin{enumerate}
\item
  Expanding the system to accommodate greater volume of use -- this
  might involve accomodating more reduction workers, for example
\item
  Integrating other methods of monitoring or listening for new runs -- the current
  method of watching a file archive is specific to ISIS
\item
  Make the WebApp accessible from outside of the laboratory
\item
  Have selected reduced data automatically catalogued in ICAT 
\item
  Improving portability and deployability of the current software; the
  state database/webapp is currently somewhat nontrivial to deploy
\item 
  Having the worker node machine as a Docker \cite{docker} image for
  easier deployment
\end{enumerate}

In the longer term, the system may be extended to listen to live streams and begin
processing data as soon as it comes off beamlines rather then waiting for files 
to be written to disk.

@@

The autoreduction system offers a convenient way of automating data reduction
on beamline instruments. It uses a scalable architecture to allow prompt
reduction of data from a large number of instruments and utilises a web app
frontend to allow users to control the reduction process manually and verify
that the correct reduction was executed.

@@

\bibitem{apache}
	Apache HTTP Server Project
	\emph{Apache},
	\url{https://httpd.apache.org/}.

@@

\bibitem{Docker}
	Docker,
	\emph{Docker},
	\url{https://www.docker.com/}
